---
title: "Package Name: BodyPackage"
author: "Beryl Kanali"
date: "2022-10-26"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{packageTemplateHC}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Package Description

This is a package created from the `bugsigdbr` package in Bioconductor.
It imports data from BugSigDB and filters the data based on body site and
condition.

This is how the package works:

-   Calls the library `bugsigdbr`

-   Imports all the data from [BugSigBD](bugsigdb.org)

-   Filters the imported data based on body site and condition.

-   Returns a dataframe of the filtered data.


## Using `BodyPackage`

A person who is interested in using the package 'BodyPackage' above:

-  Should have the `bugsigdbr` package installed.

-  Should be interested in knowing the relationship between the body site and condition or in the data filtered based on bodysite and condition


There are over 90 different body sites and over 180 conditions in the
dataset. Body site is the part of the body or matter from the body that was tested and the condition is what the species is found to have.

Body Package accepts two arguments and both arguments are strings:
-body site : part of the body, 
-condition: condition the species has.

The output of this package is a dataframe containing all
entries of the body site  and condition of choice.

For Example: We can have the body site as "oral gland" or "rectum"
             The condition can be "COVID-19" or "obesity" etc.


## Code Description

```{r}
# This is a function to print a dataframe with body site and condition
BodyPackage <- function(`body site`,'condition') {
	library(bugsigdbr)
	data <- importBugSigDB()
	df <- subset(data, `Body site` == `body site`  &
               Condition == condition)
  
	  print(df)
}
```
The first line is a comment describing the code block.
Then in the second line we are creating a function called `BodyPackage` that takes two string arguments body site and condition.
We then call the library `bugsigdbr`.
Then in the fourth line we are importing the data and calling it "data".
The fifth line describes a dataframe called df that is created from the data we imported by filtering it according to body site and condition.
In the final line we are printing the datadrame called df as our output.


## Example
This is an example to filter the body site "rectum" and condition "COVID-19".

```{r echo=TRUE}
rectumcovid <- BodyPackage("rectum", "COVID-19")
dim(rectumcovid)
```
